Prelim Outline

### 2018-08-10 prelim/outline.tex
Outline added reach goals and conclusion/summary

\paragraph{SCO SCF: Work} The task at hand was to generate low-energy states for the three different dopings x=0, 0.125, and 0.25 on a 2$\sqrt(2)$x2$\sqrt(2)$x1 unit cell and use them in our \textit{ad hoc} fitting procedure to generate an approximate effective model.
\\
\textit{This paragraph should talk about the procedural work of generating these low energy states and the mean field approximation for fitting.}

@@

 \paragraph{•}

>>>>

\paragraph{SCO SCF: Work} The task at hand was to generate low-energy states for the three different dopings x=0, 0.125, and 0.25 on a 2$\sqrt(2)$x2$\sqrt(2)$x1 unit cell and use them in our \textit{ad hoc} fitting procedure to generate an approximate effective model.
\\
\textit{This paragraph should talk about the procedural work of generating these low energy states and the mean field approximation for fitting. REMEMBER TO TALK ABOUT DROPPED STATES}

@@

 \paragraph{SCO DMD: Reach goal} A longer term goal is to use the DMD method to generate a single low-energy model that can accurately describe the low-energy properties of both superconducting SCO and an isostructural non-super conducting nickelate.
 \\
 \textit{This should talk about the goal of showing that DMD is actually accurate in its predictions, and is an interesting scientific problem not just a calculation we did.}

\section{Conclusion and Summary}
\paragraph{SCO DMD} We propose that a DMD method using \textit{ab initio} QMC calculations can generate an effective model which can describe the low-energy properties of the electron doped cuprate SCO with a level of accuracy previously unattainable.

\paragraph{SCO Reach goal} We hope to extend our model fitting calculation to gain insight into why materials like nickelates, which are isostructural to the cuprates, do not superconduct.
